AN EFFICIENT LOCALIZED MODEL ORDER REDUCTION FRAMEWORK FOR THE SHAPE OPTIMIZATION OF ADDITIVELY MANUFACTURED LATTICE STRUCTURES\break ECCOMAS CONGRESS 2024

### 2024-08-25 paper/paper.tex
[sec 2.2] wip until 2.2.1

Next, a coarse grid partition of the global domain and a fine grid partition of the unit cell is introduced as shown in~\added[id=pd]{TODO: add figure showing coarse grid and fine grid for a single unit cell.}
\added[id=pd]{Fig. XX} also shows one exemplary oversampling domain $\varOmega^{\bm\mu}$.

@@

Note that the topology is dependent on the target subdomain $\varOmega^{\m}_{\inrm}$ and the size of the oversampled region (\added[id=pd]{TODO: refer to figure as above}).

@@

The transfer operator $\bm{T}_{\m}: \mathcal{S}\to\mathcal{R}$, maps the boundary data $\bm{g}$ to the solution on the target subdomain $\bm{u}(\m)\big\vert_{\varOmega^{\p}_{\inrm}} = \bm{T}_{\m}(\bm{g}).$

@@

\added[id=pd]{Mention additional Neumann problem, data to be added to the final basis. Introduce terminology of spectral basis as part without Neumann}
% - setting, global domain = union of non overlapping subdomains = unit cells
% - introduction of coarse grid where each cell corresponds to unit cell subdomain
% - goal of constructing local spaces for only parts of the domain
% - definition of oversampling problem and transfer operator
% these are details of the specific problem we solve later
% - the oversampling problem should be formulated for union of parent unit cells
% - weak formulation is not required here? Should be first introduced in section 2.3?
% - comment on number of archetypes/configurations

\begin{figure}
    \centering
    \include{./img/oversampling_domain.tex}
    \caption{Exemplary coarse grid discretization of the global domain $\varOmega^{\m}_{\gl}$, with oversampling domain $\varOmega^{\m}$ in grey (a) and fine grid discretization of the unit cell (b).}\label{fig:oversampling_domain}
\end{figure}

@@

    \State{$\bm{S}$ $\gets\;\emptyset$}\Comment{initialize snapshot set}
    \State{$\bm{S}_{\mathrm{train}}\gets\;\{\bm\mu_1,\ldots,\bm\mu_{N_\mathrm{train}}\}$}\Comment{initialize training set}
    \For{$\bm\mu_j$ in $\bm{S}_{\mathrm{train}}$}
    \State{$\bm{R}\gets$ \textsc{AdaptiveRandomizedRangeApproximation}($\bm{T}_{\bm\mu_j}$, $\texttt{tol}$, $n_t$, $\varepsilon_{\mathrm{algofail}}$)}
    \State{$\bm{u}_{\mathrm{Neumann}}(\bm\mu_j)\gets \bm{T}_{\bm\mu_j}(\bm{0})$}\Comment{solve additional Neumann problem if $\varGamma_{\mathrm{N}}\ne\emptyset$}
    \State{$\bm{R}\gets \bm{R}\cup\left(\bm{u}_{\mathrm{Neumann}}(\bm\mu_j)\right)$}
    \State{$\bm{S}\gets \bm{S}\cup\left(\mathrm{orthonormalize}\left(\bm{R}\right)\right)$}
    \EndFor%
    \State{$\bm{B}\gets\textsc{POD}(\bm{S})$}
    \State{\textbf{return} {$X^n=\mathrm{span}\left(\bm{B}\right)$}}
    \EndFunction%
    \end{algorithmic} 
\end{algorithm}

>>>>

Next, a coarse grid partition of the global domain and a fine grid partition of the unit cell is introduced as shown in~\cref{fig:oversampling_domain}.
\Cref{fig:oversampling_domain} also shows one exemplary oversampling domain $\varOmega^{\bm\mu}$.

@@

Note that the topology is dependent on the target subdomain $\varOmega^{\m}_{\inrm}$ and the size of the oversampled region.

@@

The transfer operator $\bm{T}_{\m}: \mathcal{S}\to\mathcal{R}$, maps for a given parameter value $\m$ the boundary data $\bm{g}$ to the solution on the target subdomain $\bm{u}(\m)\big\vert_{\varOmega^{\p}_{\inrm}} = \bm{T}_{\m}(\bm{g}).$

@@

Finally, we note that the images of $\bm{T}_{\m}$ are computed, such that they do not contain any translations or rotations (rigid body modes are removed via orthogonal projection), \ie{} they comprise purely \textit{deformational modes}.
Moreover, (global) \textsc{Neumann} or \textsc{Dirichlet} boundary conditions prescribed on $\varSigma^{\m}_{\mathrm{N}}$ or $\varSigma^{\m}_{\mathrm{D}}$, respectively, have not been considered yet.
Therefore, for example, an additional \textsc{Neumann} problem\footnote{The case of inhomogeneous \textsc{Dirichlet} boundary conditions is analogous.} has to be solved to enrich the local spaces.
\begin{align}
	\begin{split}
	\label{eq:neumann_problem}
    - \div{\bm{\sigma}} (\bm{u}(\bm\mu)) &= \bm{0} \quad  \mathrm{in}\;{\varOmega^{\bm\mu}}\subset\varOmega^{\bm\mu}_{\mathrm{gl}}\,,\\
    \bm{\sigma}(\bm{u}(\bm\mu)) \vdot \bm{n} &= \hat{\bm{t}} \quad \mathrm{on}\; \varGamma^{\m}_{\mathrm{N}}:= \partial\varOmega^{\m}\cap\varSigma^{\m}_{\mathrm{N}}\,,\\
    \bm{u}(\bm\mu) &= \bm{0} \quad  \mathrm{on}\;\varGamma^{\m}_{\mathrm{D}}:=\partial\varOmega^{\m}\cap\varSigma^{\m}_{\mathrm{D}}\,,\\
    \bm{u}(\bm\mu) &= \bm{0}\quad\mathrm{on}\;\varGamma^{\m}_{\mathrm{out}}:= \partial\varOmega^{\m} \setminus\partial\varOmega^{\m}_{\mathrm{gl}}\,.
	\end{split}
\end{align}
\Cref{eq:neumann_problem} is solved on the parent domain employing a pull back as above.
Also, for construction of a sufficiently rich local basis it has to be solved for many parameter values $\m$, but a sampling of the boundary values on $\varGamma^{\m}_{\out}$ is not required.
% - setting, global domain = union of non overlapping subdomains = unit cells
% - introduction of coarse grid where each cell corresponds to unit cell subdomain
% - goal of constructing local spaces for only parts of the domain
% - definition of oversampling problem and transfer operator
% these are details of the specific problem we solve later
% - the oversampling problem should be formulated for union of parent unit cells
% - weak formulation is not required here? Should be first introduced in section 2.3?
% - comment on number of archetypes/configurations

\begin{figure}
    \centering
    \include{./img/oversampling_domain.tex}
    \caption{Exemplary coarse grid discretization of the global domain $\varOmega^{\m}_{\gl}$, with target subdomain $\varOmega^{\m}_i$ within oversampling domain $\varOmega^{\m}$ in grey (a) and fine grid discretization of the unit cell (b).}\label{fig:oversampling_domain}
\end{figure}

@@

    \State{$\bm{S}$ $\gets\;\emptyset$}\Comment{initialize snapshot set}
    \State{$\bm{S}_{\mathrm{train}}\gets\;\{\bm\mu_1,\ldots,\bm\mu_{N_\mathrm{train}}\}$}\Comment{initialize training set}
    \For{$\bm\mu_j$ in $\bm{S}_{\mathrm{train}}$}
    \State{$\bm{R}\gets$ \textsc{AdaptiveRandomizedRangeApproximation}($\bm{T}_{\bm\mu_j}$, $\texttt{tol}$, $n_t$, $\varepsilon_{\mathrm{algofail}}$)}
    % \State{$\bm{u}_{\mathrm{Neumann}}(\bm\mu_j)\gets \bm{T}_{\bm\mu_j}(\bm{0})$}\Comment{solve additional Neumann problem if $\varGamma_{\mathrm{N}}\ne\emptyset$}
    % \State{$\bm{R}\gets \bm{R}\cup\left(\bm{u}_{\mathrm{Neumann}}(\bm\mu_j)\right)$}
    \State{$\bm{S}\gets \mathrm{orthonormalize}\left(\bm{S}\cup\bm{R}\right)$}
    \EndFor%
    \State{$\bm{B}\gets\textsc{POD}(\bm{S})$}
    \State{\textbf{return} {$X^n=\mathrm{span}\left(\bm{B}\right)$}}
    \EndFunction%
    \end{algorithmic} 
\end{algorithm}
